Introduction_outline

### 2019-01-13 Write_up/Writing/Introduction_outline.Rmd
edited

Seawater temperature is a key indicator of environmental change in both terrestrial and marine ecosystems (Pearce et al., 2006), which directly influences the earth’s natural ecological functioning. Climate change is widely believed to result in a rise in the earth’s average surface temperatures over time (Stocker et al., 2013) and this is usually associated with an increase in the intensity and duration of extreme weather events such as cold-spells, heatwaves, floods and storms. Consequently, these extreme climatic events can often have profound short-term effects on both humans as well as many ecosystems (Easterling et al., 2000).

>>>>

Seawater temperature is a key indicator of environmental change in both terrestrial and marine ecosystems (Pearce et al., 2006), which directly influences the earth’s natural ecological functioning. Climate change is widely believed to result in a rise in the earth’s average surface temperatures over time (Stocker et al., 2013) and this is usually associated with an increase in the intensity and duration of extreme events such as cold-spells, heatwaves, floods and storms. Consequently, these extreme climatic events can often have profound short-term effects on both humans as well as many ecosystems (Easterling et al., 2000).
